---
title: "Portfolio_2"
author: "Sofie Bøjgaard Thomsen"
date: "2024-10-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Synthesize the data set
https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/effects.html#s-md

To conduct a meta-analysis of standardized mean differences, our data set should at least contain the following columns:

n.e. The number of observations in the intervention/experimental group.
mean.e. The mean of the intervention/experimental group.
sd.e. The standard deviation in the intervention/experimental group.
n.c. The number of observations in the control group.
mean.c. The mean of the control group.
sd.c. The standard deviation in the control group.

```{r}
# Install and load esc package
install.packages("esc")
library(esc)
```

# Combining effect sizes from multiple studies

#Loading package
```{r}
# Load necessary package
install.packages("meta")
library(meta)
```

#Loading data from TST
```{r}
TST <- read.csv("meta/raw-data-extraction - TST.csv")

# Using metacont to pool results
m.tst <- metacont(n.e = hc_n,
                   mean.e = hc_m,
                   sd.e = hc_sd,
                   n.c = nc_n,
                   mean.c = nc_f_m,
                   sd.c = nc_f_sd,
                   studlab = Article,
                   data = TST,
                   sm = "SMD",
                   method.smd = "Hedges",
                   fixed = FALSE,
                   random = TRUE,
                   method.tau = "DL",
                   method.random.ci = "HK",
                   title = "Total sleep time, min")

m.tst <- update(m.tst, prediction = TRUE)
summary(m.tst)
```


#Loading data from TIB
```{r}
TIB <- read.csv("meta/raw-data-extraction - TIB.csv")

# Using metacont to pool results
m.tib <- metacont(n.e = hc_n,
                   mean.e = hc_m,
                   sd.e = hc_sd,
                   n.c = nc_n,
                   mean.c = nc_f_m,
                   sd.c = nc_f_sd,
                   studlab = Article,
                   data = TIB,
                   sm = "SMD",
                   method.smd = "Hedges",
                   fixed = FALSE,
                   random = TRUE,
                   method.tau = "DL",
                   method.random.ci = "HK",
                   title = "Total time in bed, min")

m.tib <- update(m.tib, prediction = TRUE)
summary(m.tib)
```

#Loading data from SWS
```{r}
SWS <- read.csv("meta/raw-data-extraction - SWS.csv")

# Using metacont to pool results
m.sws <- metacont(n.e = hc_n,
                   mean.e = hc_m,
                   sd.e = hc_sd,
                   n.c = nc_n,
                   mean.c = nc_f_m,
                   sd.c = nc_f_sd,
                   studlab = Article,
                   data = SWS,
                   sm = "SMD",
                   method.smd = "Hedges",
                   fixed = FALSE,
                   random = TRUE,
                   method.tau = "DL",
                   method.random.ci = "HK",
                   title = "Percentage of slow wave sleep")

m.sws <- update(m.sws, prediction = TRUE)
summary(m.sws)
```

#Loading data from SOL
```{r}
SOL <- read.csv("meta/raw-data-extraction - SOL.csv")

# Using metacont to pool results
m.sol <- metacont(n.e = hc_n,
                   mean.e = hc_m,
                   sd.e = hc_sd,
                   n.c = nc_n,
                   mean.c = nc_f_m,
                   sd.c = nc_f_sd,
                   studlab = Article,
                   data = SOL,
                   sm = "SMD",
                   method.smd = "Hedges",
                   fixed = FALSE,
                   random = TRUE,
                   method.tau = "DL",
                   method.random.ci = "HK",
                   title = "Sleep onset latency, min")

m.sol <- update(m.sol, prediction = TRUE)
summary(m.sol)
```

#Loading data from SEff
```{r}
SEff <- read.csv("meta/raw-data-extraction - SEff.csv")

# Using metacont to pool results
m.seff <- metacont(n.e = hc_n,
                   mean.e = hc_m,
                   sd.e = hc_sd,
                   n.c = nc_n,
                   mean.c = nc_f_m,
                   sd.c = nc_f_sd,
                   studlab = Article,
                   data = SEff,
                   sm = "SMD",
                   method.smd = "Hedges",
                   fixed = FALSE,
                   random = TRUE,
                   method.tau = "DL",
                   method.random.ci = "HK",
                   title = "Sleep efficiency, %")

m.seff <- update(m.seff, prediction = TRUE)
summary(m.seff)
```


#Loading data from ROL
```{r}
ROL <- read.csv("meta/raw-data-extraction - ROL.csv")

# Using metacont to pool results
m.rol <- metacont(n.e = hc_n,
                   mean.e = hc_m,
                   sd.e = hc_sd,
                   n.c = nc_n,
                   mean.c = nc_f_m,
                   sd.c = nc_f_sd,
                   studlab = Article,
                   data = ROL,
                   sm = "SMD",
                   method.smd = "Hedges",
                   fixed = FALSE,
                   random = TRUE,
                   method.tau = "DL",
                   method.random.ci = "HK",
                   title = "REM sleep latency, min")

m.rol <- update(m.rol, prediction = TRUE)
summary(m.rol)
```

#Loading data from REM
```{r}
REM <- read.csv("meta/raw-data-extraction - REM.csv")

# Using metacont to pool results
m.rem <- metacont(n.e = hc_n,
                   mean.e = hc_m,
                   sd.e = hc_sd,
                   n.c = nc_n,
                   mean.c = nc_f_m,
                   sd.c = nc_f_sd,
                   studlab = Article,
                   data = REM,
                   sm = "SMD",
                   method.smd = "Hedges",
                   fixed = FALSE,
                   random = TRUE,
                   method.tau = "DL",
                   method.random.ci = "HK",
                   title = "Percentage of REM sleep")


m.rem <- update(m.rem, prediction = TRUE)
summary(m.rem)
```


#Loading data from N2
```{r}
N2 <- read.csv("meta/raw-data-extraction - N2.csv")

# Using metacont to pool results
m.n2 <- metacont(n.e = hc_n,
                   mean.e = hc_m,
                   sd.e = hc_sd,
                   n.c = nc_n,
                   mean.c = nc_f_m,
                   sd.c = nc_f_sd,
                   studlab = Article,
                   data = N2,
                   sm = "SMD",
                   method.smd = "Hedges",
                   fixed = FALSE,
                   random = TRUE,
                   method.tau = "DL",
                   method.random.ci = "HK",
                   title = "Percentage of stage 2 sleep")

m.n2 <- update(m.n2, prediction = TRUE)
summary(m.n2)
```

# Making and saving forest plots

#First for TST
```{r}
png(file = "meta/TST.png", width = 3200, height = 1100, res = 300)

meta::forest(m.tst, 
             sortvar = TE,
             prediction = TRUE, 
             print.tau2 = FALSE,
             leftlabs = c("Author", "g", "SE"))

dev.off()
```

# Then for TIB
```{r}
png(file = "meta/TIB.png", width = 3200, height = 1100, res = 300)

meta::forest(m.tib, 
             sortvar = TE,
             prediction = TRUE, 
             print.tau2 = FALSE,
             leftlabs = c("Author", "g", "SE"))

dev.off()
```

# Then for SWS
```{r}
png(file = "meta/SWS.png", width = 3200, height = 1100, res = 300)

meta::forest(m.sws, 
             sortvar = TE,
             prediction = TRUE, 
             print.tau2 = FALSE,
             leftlabs = c("Author", "g", "SE"))

dev.off()
```

# Then for SOL
```{r}
png(file = "meta/SOL.png", width = 3200, height = 1100, res = 300)

meta::forest(m.sol, 
             sortvar = TE,
             prediction = TRUE, 
             print.tau2 = FALSE,
             leftlabs = c("Author", "g", "SE"))

dev.off()
```

# Then for SEff
```{r}
png(file = "meta/SEff.png", width = 3200, height = 1100, res = 300)

meta::forest(m.seff, 
             sortvar = TE,
             prediction = TRUE, 
             print.tau2 = FALSE,
             leftlabs = c("Author", "g", "SE"))

dev.off()
```

# Then for ROL
```{r}
png(file = "meta/ROL.png", width = 3200, height = 1100, res = 300)

meta::forest(m.rol, 
             sortvar = TE,
             prediction = TRUE, 
             print.tau2 = FALSE,
             leftlabs = c("Author", "g", "SE"))

dev.off()
```

# Then for REM
```{r}
png(file = "meta/REM.png", width = 3200, height = 1100, res = 300)

meta::forest(m.rem, 
             sortvar = TE,
             prediction = TRUE, 
             print.tau2 = FALSE,
             leftlabs = c("Author", "g", "SE"))

dev.off()
```

# Lastly, for stage 2 of sleep
```{r}
png(file = "meta/N2.png", width = 3200, height = 1100, res = 300)

meta::forest(m.n2, 
             sortvar = TE,
             prediction = TRUE, 
             print.tau2 = FALSE,
             leftlabs = c("Author", "g", "SE"))

dev.off()
```


```{r}
citation()
```

